Hydras \& Co.

### 2021-12-28 doc/hydras.tex
new title page

       \textbf{\LARGE Hydras \& Co.}

       \vspace{0.5cm}
        Formalized mathematics in \coq for inspiration and entertainement

@@

       \emph{Pierre Castéran, LaBRI, Univ. Bordeaux, CNRS UMR 5800, \\ With contributions by Yves Bertot, \'Evelyne Contejean,  Jérémy Damour, Florian Hatat, Pascal Manoury, Karl Palmskog, Clément Pit-Claudel, and Théo Zimmermann. \\ The formalization of primitive recursive functions was originally authored by Russel O'Connor\cite{OConnor05}.}

@@

      \end{center}
\vfill
      \centering
      \includegraphics[width=13cm]{epsilon0.jpg}
      \centerline{\emph{\small {\color{darkblue}Ordinal numbers (less than $\Gamma_0$)}}}
\end{titlepage}

@@

\section{How to install the libraries}
\label{sec:orgheadline4}
\begin{itemize}
\item The present distribution has been checked with version 8.13.2 of the Coq proof assistant, with the plug-ins \texttt{coq-paramcoq}, \texttt{coq-equations}
and \texttt{coq-mathcomp-algebra}.

@@

Many thanks also to the Coq development team, Yves Bertot, and the members of the \emph{Coq Club} for interesting discussions about the \coq{} system and the Calculus of Inductive Constructions.

>>>>

       \textbf{\Huge Hydras \& Co.}

       \vspace{0.5cm}
        {\emph{\Large Formalized mathematics in \coq for inspiration and entertainement}}

@@

       \emph{Pierre Castéran, LaBRI, Univ. Bordeaux, CNRS UMR 5800, \\ With contributions by Yves Bertot, \'Evelyne Contejean,  Jérémy Damour, Florian Hatat, Pascal Manoury, Karl Palmskog, Clément Pit-Claudel, and Théo Zimmermann. \\ The formalization of primitive recursive functions was originally authored by Russel O'Connor.}%\cite{OConnor05}.}

@@

      \end{center}
\vfill
      \centering
      \includegraphics[width=13cm]{epsilon0.jpg}
      \centerline{\emph{\small {\color{darkblue}Ordinal numbers in Veblen normal form}}}
\end{titlepage}

@@

\section{How to install the libraries}
\label{sec:orgheadline4}
\begin{itemize}
\item The present distribution has been checked with version 8.14.1 of the Coq proof assistant, with the plug-ins \texttt{coq-paramcoq}, \texttt{coq-equations}
and \texttt{coq-mathcomp-algebra}.

@@

Many thanks also to the Coq development team and the members of the \emph{Coq Club} for interesting discussions about the \coq{} system and the Calculus of Inductive Constructions.
